Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-20 papers/B1555_EdgeOn/B1555_letter.tex
update 2-SIE paras to text
Small updates to text

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure.

An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this paper, we explore the alternative idea that flux ratio anomalies
are not related to the presence of substructure but originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program(SHARP). The main goal of
the SHARP project is to re-observe known quadruple and Einstein ring
lens systems at a much higher angular resolution by making use of the
Keck adaptive optics (AO) telescope and large interferometric arrays
\citep{SHARP12,V12} . In particular, to better understand the cause of
flux ratio anomalies in strong lens systems we focus on the lens
modelling of the lens system B1555+375 (included in both the
observational and theoretical analysis of \citet{Dalal2002} and
\citet{Xu14}, respectively) by making use of the new information
obtained from the latest SHARP infrared imaging. The paper is
organized as follows: the latest SHARP data is introduced in section
2; in section 3 we present the lens model while the results of this
analysis and their implication are discussed in section 4.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$141.3$ &	$144.6$	  \\
$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$123.8$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\hline
\end{tabular}

@@

%\end{minipage}
\medskip
Comparision between radio data and model-predicted flux ratios. Radio observation data is quoted from Table 2 and Table 3 in \citet{Marlow}. 1-SIE model is quoted from Tabel 5 in \citet{Marlow}.

@@

We present new lens models of B1555+375. With the new imaging from SHARP $K^{\prime}$ band, the most significant difference comparing to previous modelling is a new edge-on disk component. With a bulge plus an edge-on disk, our models fairly match to the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail. Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}. Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375. An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues. This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations. It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in a strongly lensed system.

>>>>

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. 
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this paper, we explore the idea that not all flux ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program (SHARP; Fassnacht et al.,
in prep). The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at a much higher angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, to better
understand the causes of flux ratio anomalies in gravitational lenses
we focus on the B1555+375 lens system\citep{Marlow}.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong flux ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importantce.  Our analysis makes use of
the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the latest SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1883$	& $-0.1809$  \\
$y_1$	  &$-0.1923$	&$-0.1702$  \\
$x_2$	  &$-0.1615$ 	&$-0.1592$  \\
$y_2$	  &$-0.2502$	& $-0.1833$  \\
$\sigma_1$ &$141.3$     & $144.6$ \\
$e_1$	  & $0.27$	& $0.27$ \\
$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$123.8$ \\  
$e_2$	  &$0.84$	&$0.83$  \\
$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
$r_e$	  & $0.20 ''$ &  ... \\
\hline
\end{tabular}

@@

%\end{minipage}
\medskip
Comparision between radio data and model-predicted flux ratios. The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow}. 1-SIE model is quoted from Tabel 5 in \citet{Marlow}.

@@

In our models based on the new imaging from the SHARP $K^{\prime}$
band observations, the most significant difference in comparison to
previous modelling is a new edge-on disk component. With a bulge plus
an edge-on disk, our models produce matches to both the radio image
positions and flux ratio anomalies, while models with only one SIE
component \citep{Marlow,Xu14} fail to reproduce the fluxes
correctly. Our successful modelling indicates that the
kiloparsec-scale structure of lens galaxy itself is sufficient to
explain the flux ratio anomalies in B1555+375, without any need to
invoke the presense of substructrue. This breaks the idea that in
strongly lensed quasars, radio flux ratio anomalies are most likely
originated from substructure perturbations. It is worth noticing not
all of flux ratio anomalies in lensed quasars indicate the existence
of substructures. Our discovery shows a complex lens galaxy mass
distribution can dominate flux ratio anomalous phenomena in a strongly
lensed system.
